Adaptive Sequential Model Selection

### 2015-07-21 paper.tex
robs small changes

Given a model $M_{k-1}$   we need to sample from 
\begin{eqnarray}
L(X'_jY | E_{k-1},X'_{E_{k-1}})
\label{eqn:maxtsamp}
\end{eqnarray}
with $Y\sim N(\mu, I \cdot \sigma^2)$.
The current model fit is $\proj_{E_{k-1}} Y$ and it is easy to see that (\ref{eqn:maxtsamp})  is equivalent to sampling
\begin{eqnarray}
Y^*=\proj_{E_{k-1}} Y + (I- \proj_{E_{k-1}}) Z; \;Z\sim N(0,I\cdot\sigma^2)
\label{eq:boot}
\end{eqnarray}
and then conditioning on the event $E_{k-1}(Y^*)= E_k(Y)$ (a polyhedron).
In other words, we need to condition on data vectors  $Y*$ that yields the same
sequence of variables and coefficient signs up to step $k-1$. This is the challenging aspect of this computation.

@@

In detail, we employ a hybrid computational strategy; we use accept-reject sampling, and do so as long as we obtain at least 300 (say) samples in the first set
of $B$ realizations ($75,000$ in our code)  This is an effective approach until we have reached a point in the model path where all predictors have little or no signal.
When the acceptance rate gets too low, we switch to a hit-and run Monte Carlo approach. We exploit the fact that each move along a random direction 
has a truncated Gaussian distribution whose truncation limits are easily computed from the properties of the polyhedral. Unlike accept-reject, sampling
which produces independent samples,  the hit and run method produces dependent samples. Hence we must run it for longer with an initial burn in period,
and hope that it has mixed sufficiently well.

>>>>

Given a model $M_{k-1}$   we need to sample from 
\begin{eqnarray}
L(X'_jY | E_{k-1},X'_{E_{k-1}}Y)
\label{eqn:maxtsamp}
\end{eqnarray}
with $Y\sim N(\mu, I \cdot \sigma^2)$.
The current model fit is $\proj_{E_{k-1}} Y$ and it is easy to see that (\ref{eqn:maxtsamp})  is equivalent to sampling
\begin{eqnarray}
Y^*=\proj_{E_{k-1}} Y + (I- \proj_{E_{k-1}}) Z; \;Z\sim N(0,I\cdot\sigma^2)
\label{eq:boot}
\end{eqnarray}
and then conditioning on the event $E_{k-1}(Y^*)= E_k(Y)$ (a polyhedron).
In other words, we need to condition on data vectors  $Y^*$ that yields the same
sequence of variables and coefficient signs up to step $k-1$. This is the challenging aspect of this computation.

@@

In detail, we employ a hybrid computational strategy; we use accept-reject sampling, and do so as long as we obtain at least 300 (say) samples in the first set
of $B$ realizations ($75,000$ in our code)  This is an effective approach until we have reached a point in the model path where all predictors have little or no signal.
When the acceptance rate gets too low, we switch to a hit-and run Monte Carlo approach. We exploit the fact that each move along a random direction 
has a truncated Gaussian distribution whose truncation limits are easily computed from the properties of the polyhedron. Unlike accept-reject, sampling
which produces independent samples,  the hit and run method produces dependent samples. Hence we must run it for longer with an initial burn in period,
and hope that it has mixed sufficiently well.
